Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-08-25 manuscript.tex
Better figure letters in split and caption
Added part describing errors in glq

%\documentclass[extra,mreferee]{gji}
% Use the option below to make a nicely formatted manuscript
\documentclass[extra]{gji}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:tesseroid}
\end{figure}

@@

THE EFFECTS OF THE NUMBER OF NODES AND DISTANCE ON THE COMPUTATIONS.

@@

We have developed a modified version
of the recursive division scheme of \citet{Li2011}.
We fix the number of nodes in the GLQ
$N^\lambda=N^\phi=N^r=2$
so that the distance between nodes
in the radial, longitudinal, and latitudinal directions
are approximately the dimensions of the tesseroid
\citep{Wild-Pfeiffer2008}.
We define the distance $d$ as
the Cartesian distance between
the computation point $P$
and the center of the top face of the tesseroid
(Fig.~\ref{fig:ratio}a).

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using $R$ equal to
        (b) 1, (c) 2, and (d) 6.
        $d$ is the distance between
        the center of the top face of the tesseroid
        and $P$.
        $L$ is the largest dimension of the tesseroid.
    }
    \label{fig:ratio}
\end{figure}

>>>>

\documentclass[extra,mreferee]{gji}
% Use the option below to make a nicely formatted manuscript
%\documentclass[extra]{gji}

@@

\begin{figure}
    \centering
    \includegraphics{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:tesseroid}
\end{figure}

@@

The accuracy of the integration
depends on the number of nodes, or GLQ order,
used in the discretization.
However, \citet{Ku1977} showed
that it also depends on the ratio between
the distance to the computation point
and the distance between adjacent nodes.
Fig.~\ref{fig:sample}
illustrates this effect.
To increase the accuracy of the integration,
one could increase the number of nodes,
as in Fig.~\ref{fig:sample}c.
Likewise,
one could keep the number of nodes fixed
and instead divide the tesseroid into smaller ones.
This would increase the total number of nodes
and effectively decrease
the distance between adjacent nodes.
The latter is the approach
taken by \citet{Li2011}.
Here, we will follow the same approach
and make some improvements to the algorithm.
We will also attempt to quantify
the error committed in the numerical integration.

@@

We have developed a modified version
of the recursive division algorithm of \citet{Li2011}.
We fix the number of nodes in the GLQ
$N^\lambda=N^\phi=N^r=2$
so that the distance between nodes
in the radial, longitudinal, and latitudinal directions
are approximately the dimensions of the tesseroid
\citep{Wild-Pfeiffer2008}.
We define the distance $d$ as
the Cartesian distance between
the computation point $P$
and the center of the top face of the tesseroid
(Fig.~\ref{fig:ratio}a).

@@

\begin{figure}
    \centering
    \includegraphics{figs/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using $R$ equal to
        (b) 1, (c) 2, and (d) 6.
        $d$ is the distance between
        the center of the top face of the tesseroid
        and $P$.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
    }
    \label{fig:ratio}
\end{figure}
